Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-04-24 Paper.tex
Add more clear explanation for out-of-gas exception
7. Contract Creation
https://github.com/ethereum/yellowpaper/blob/934279c87ab7e58c4d06f4042642afcfdab1f412/Paper.tex#L877
Add more clear explanation of exception
fix(sec. 9.2): Added two of the CALL opcodes
All CALLs caused a subordinate message call.

Fees (denominated in gas) are charged under three distinct circumstances, all three as prerequisite to the execution of an operation. The first and most common is the fee intrinsic to the computation of the operation (see Appendix \ref{app:fees}). Secondly, gas may be deducted in order to form the payment for a subordinate message call or contract creation; this forms part of the payment for {\small CREATE}, {\small CREATE2}, {\small CALL} and {\small CALLCODE}. Finally, gas may be paid due to an increase in the usage of the memory.

>>>>

Fees (denominated in gas) are charged under three distinct circumstances, all three as prerequisite to the execution of an operation. The first and most common is the fee intrinsic to the computation of the operation (see Appendix \ref{app:fees}). Secondly, gas may be deducted in order to form the payment for a subordinate message call or contract creation; this forms part of the payment for {\small CREATE}, {\small CREATE2}, {\small CALL}, {\small CALLCODE}, {\small DELEGATECALL}, and {\small STATICCALL}. Finally, gas may be paid due to an increase in the usage of the memory.
